Methods for Large Scale Learning to Rank

### 2014-04-14 report/Chapters/BenchmarkResults.tex
AOL mirror footnot
Yandex IMC

\subsection{AOL}
Pass et al. \cite{Pass2006} describe an America Online Learning-to-Rank dataset which they published in 2006. This dataset is unique in that it is the only large commercial web search dataset that contains user session and user behaviour information. The dataset contains 20 million search keywords for over 650,000 users over a three month time period. AOL later realised the publication of the dataset to be a mistake, as personally identifiable information turned out to be presented in some of the queries\footnote{http://select.nytimes.com/gst/abstract.html?res=F10612FC345B0C7A8CDDA10894DE404482}. AOL acknowledged the mistake of publishing the data and removed the data from its website. The removal of the data was too late, as the data was already downloadable from several mirror sites. This controversial AOL dataset is to date still used for Learning-to-Rank research. No official baseline evaluation is provided by the AOL team.

\subsection{Yandex Internet Mathematics competition}
%TODO: YIMC beschrijven
The Yandex Internet Mathematics competition was won by Pavlov et al. \cite{Pavlov2010} with the BagBoo method.

>>>>

\subsection{AOL}
Pass et al. \cite{Pass2006} describe an America Online Learning-to-Rank dataset which they published in 2006. This dataset is unique in that it is the only large commercial web search dataset that contains user session and user behaviour information. The dataset contains 20 million search keywords for over 650,000 users over a three month time period. AOL later realised the publication of the dataset to be a mistake, as personally identifiable information turned out to be presented in some of the queries\footnote{http://select.nytimes.com/gst/abstract.html?res=F10612FC345B0C7A8CDDA10894DE404482}. AOL acknowledged the mistake of publishing the data and removed the data from its website. The removal of the data was too late, as the data was already downloadable from several mirror sites\footnote{http://gregsadetsky.com/aol-data/}. This controversial AOL dataset is to date still used for Learning-to-Rank research. No official baseline evaluation is provided by the AOL team.

\subsection{Yandex Internet Mathematics contest}
Russian commercial web search engine Yandex dedicated their yearly Internet Mathematics contest to the task of Learning-to-Rank in the 2009 edition of the contest. Features (245 in total) are only numbered and their semantics are not revealed, equivalent to the Yahoo! Learning to Rank Challenge. The set is split into a 45\%-training, 10\%-validation, and 45\%-test data. The training set contains 9124 queries, with on average around 100 assessed documents per query. Yandex IMC 2009 has an online leaderboard\footnote{http://imat2009.yandex.ru/en/results} showing the best performing teams in the contest, but it is not traceable which methods each teams used. Pavlov et al. \cite{Pavlov2010} in their paper claim to have won the Yandex Internet Mathematics contest 2009 with their BagBoo method.
